### 2016-12-01 thesis/intro/intro.tex
tmp commit

>>>>

As mentioned briefly in \cref{sub:causes_and_risk_factors_of_cancer}: \nameref{sub:causes_and_risk_factors_of_cancer}, obesity is considered a major risk factor for many, if not all, types of cancers.
The fact that the prevalence of obesity is extremely high, it is important to establish the link between the apparent risks associated with cancer.
